Advancing Renewable Gas Storage using Flat-histogram Methods

### 2020-05-29 dissertation/introduction.tex
added a new dissertation tex which conforms to OSU guidlines.
made changes to thesis and cover letter.

\chapter{Introduction}

@@

In our works, we use the \textbf{Xoroshiro128+} RNG which is named after its logical operations (XOR $\xrightarrow{}$ rotate $\xrightarrow{}$ shift $\xrightarrow{}$ rotate). The RNG has ultra-fast speed 0.72 $\nicefrac{\text{ns}}{\text{64-bits}}$ and incredible statistical quality~\cite{blackman2018scrambled}.

>>>>

@@

In our work, we use the \textbf{Xoroshiro128+} RNG which is named after its logical operations (XOR $\xrightarrow{}$ rotate $\xrightarrow{}$ shift $\xrightarrow{}$ rotate). The RNG has ultra-fast speed 0.72 $\nicefrac{\text{ns}}{\text{64-bits}}$ and incredible statistical quality~\cite{blackman2018scrambled}.
